Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-09-18 paper/analysis.tex
rework and correct stable rank remark

\begin{remark}
    If $\mtx{A}(t)$ is nonzero and symmetric positive semi-definite for all $t \in [a, b]$, then it follows that with probability at least $1 - \delta$
    \begin{equation}
        \int_{a}^{b} \frac{| \Trace(\mtx{A}(t)) - \Hutch{\mtx{\Psi}}(\mtx{A}(t)) |}{\Trace(\mtx{A}(t))} ~\mathrm{d}t < \varepsilon,
    \end{equation}
    if $n_{\mtx{\Psi}} \geq 2 c^2 e^2 \log(\delta^{-1}) \varepsilon^{-2} (\int_{a}^{b} \mu(t)^{\sfrac{1}{2}}~\mathrm{d}t)^2$ where $\mu(t) = \lVert \mtx{A}(t) \rVert _2 / \Trace(\mtx{A}(t))$. Up to constant factors, this matches the equivalent result for constant matrices from \cite[Remark 2]{cortinovis-2022-randomized-trace}.
\end{remark}

>>>>

\begin{remark}
    If $\mtx{A}(t)$ is nonzero and symmetric positive semi-definite for all $t \in [a, b]$, then it follows that with probability at least $1 - \delta$
    \begin{equation}
        \int_{a}^{b} \frac{| \Trace(\mtx{A}(t)) - \Hutch{\mtx{\Psi}}(\mtx{A}(t)) |}{\Trace(\mtx{A}(t))} ~\mathrm{d}t < \varepsilon,
    \end{equation}
    if $n_{\mtx{\Psi}} \geq 2 c^2 e^2 \log(\delta^{-1}) \varepsilon^{-2} (\int_{a}^{b} \eta(t)~\mathrm{d}t)^2$ where $\eta(t) = \lVert \mtx{A}(t) \rVert _F / \Trace(\mtx{A}(t))$. The quantity $\eta(t) \in [1/\sqrt{n}, 1]$ is small when the spectrum of $\mtx{A}(t)$ decays slowly and large when $\mtx{A}(t)$ when it decays quickly, i.e. $\mtx{A}(t)$ has low numerical rank. This parallels a similar result for constant matrices in~\cite[Remark 2]{cortinovis-2022-randomized-trace}.
\end{remark}
